---
title: "Chapter 6"
author: "Tao Huang"
output: 
  pdf_document:
    #toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, echo=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
library(formattable)
library(kableExtra)
library(dplyr)
library(magrittr)
library(prettydoc)
library(htmltools)
library(knitcitations)

#Generate BibTex citation file for all R packages used to produce report
knitr::write_bib(.packages(), file = 'packages.bib')
```

# 6.1.1 R Make-like files
## Example R make-like file
## Sourcing functions is good practice because it is:
## Reusable: It allows you to reuse functions over and over using the same code (i.e. you don’t have to copy and paste the function into each new analysis script).
## Easy to Maintain: It allows you to quickly fix a function that doesn’t work properly - only once.
## Sharable: In the same way that a library can be used by anyone, you can share your R script containing your functions with anyone, too. This is the first step towards creating an R package!
### https://www.earthdatascience.org/courses/earth-analytics/multispectral-remote-sensing-data/source-function-in-R/
```{r}
# Set working directory
setwd("/Users/owner/Desktop/EEB603/Ch6")
source("plot.R")
plot_density(1,2)
```

# 6.2 Importing Locally Stored Data Sets
## .csv
### read.csv
```{r}
tick<-read.csv("/Users/owner/Desktop/EEB603/Ch6/neon_CLBJ_Dermacentor.csv",sep=",",header = T)
head(tick)
```
### read.table
```{r}
tick2<-read.table("/Users/owner/Desktop/EEB603/Ch6/neon_CLBJ_Dermacentor.csv",sep=",",header = T)
head(tick2)
```

### write.csv

## .Rdata
### load()
### save()

# 6.3 Importing Data Sets from the Internet
## 6.3.1 Data from non-secure (http) URLs
```{r}
tick3<-read.csv("https://raw.githubusercontent.com/th2018/EEB603_ch6/master/neon_HARV_Dermacentor.csv")
head(tick3)
```

# 6.3.4 Data APIs & feeds
```{r}
# install neonUtilities - can skip if already installed
#install.packages("neonUtilities")
# load neonUtilities
library(neonUtilities)

```

## The identifier of the NEON data product: https://data.neonscience.org/data-products/explore
```{r}
zipsByProduct(dpID="DP1.20093.001", #Chemical properties of surface water
              site="BIGC", #Upper Big Creek, CA
              startdate = "2019-01", enddate = "2019-04",
              check.size = FALSE #R would ask you to approve the file size
              #,package = "basic", avg = "all", savepath = NA,load = F
  )
```

# 6.4 Advanced Automatic Data Gathering: Web Scraping
```{r echo=FALSE}

```
